Hydras \& Co.

### 2022-03-09 doc/gaia-chapter.tex
add compatibility notes (Gaia)
Minor corrections; add a bibitem (Talia Ringer et al.)

  We plan to make accessible the first kind of lemmas to \HydrasLib' users and the second kind to \gaia's. For this purpose, we write modules dedicated to the importation of definitions and lemmas from each of both libraries into the other one.
Please note that by ``import'' we do not mean ``duplicate the proofs''.  Whenever possible, we proceed by rewriting steps over the statements and not the proofs.

This initial draft bridge code mostly uses the SSReflect proof language
and idioms from the Mathematical Components library. We made this design
decision since we believe it is less challenging to reason about
Hydra-battles code using SSReflect and MathComp than to reason about
Gaia without SSReflect \footnote{The author of these proof scripts is still a beginner in Ssreflect. Please forgive the clumsiness of the current proof scripts.}.

@@

\subsubsection{Kind of refinement}

@@

\subsubsection{Addition and multiplication}

@@

\subsubsection{Remark}
\label{sect:gaia-masking}
We try to respect the following ``protocol''.
Let us assume we adapt some definitions and properties
from a given module \texttt{hydras.Epsilon0.{\it XXX}}.
\begin{enumerate}
\item We create a module \texttt{gaia\_hydras.{\it GXXX}},
\item When we import some constant \emph{Id} from
 \texttt{hydras.Epsilon0.{\it XXX}}, the name 
\emph{Id} is given to \texttt{gaia\_hydras.{\it GXXX.Id}}.
In order to get
\texttt{hydras.Epsilon0.{\it XXX}}'s sense, please refer it as
  \emph{XXX.Id} or \emph{Epsilon0.XXX.Id}.
  \item Sometimes, we rename \emph{XXX.Id} into \emph{{\bf h}Id} (for readability's sake).
\end{enumerate}

>>>>

  We plan to make accessible the first kind of lemmas to \HydrasLib' users and the second kind to \gaia's. For this purpose, we write modules dedicated to the importation of definitions and lemmas from each of both libraries into the other one.
  Please note that by ``import'' we do not mean ``duplicate''
  nor ``repairing'' \HydrasLib' proofs.  Whenever possible, we proceed by rewriting steps over the statements and not the proofs. In a future version, it would be nice to have our proofs in the same context, after porting \HydrasLib' proofs under \gaia's
  definition, following  proof repair  techniques~\cite{ringer2021}.

This initial draft bridge code mostly uses the SSReflect proof language
and idioms from the Mathematical Components library. We made this design
decision since we believe it is less challenging to reason about
Hydra-battles code using SSReflect and MathComp than to reason about
Gaia without SSReflect\footnote{The author of these proof scripts is still a beginner in Ssreflect. Please forgive the clumsiness of the current proof scripts.}.

@@

\subsubsection{Cancel lemmas}

\subsubsection{Refinements: Definitions}

@@

\subsubsection{Addition and multiplication}
\label{sect:plus-mult-gaia-hydras}

@@

\subsubsection{Remark}
\label{sect:gaia-masking}
We try to respect the following ``protocol''.
Let us assume we adapt some definitions and properties
from a given module \texttt{hydras.Epsilon0.Foo}, and a constant \texttt{bar} of this module, whose absolute name is
thus \texttt{hydras.Epsilon0.Foo.bar}.
\begin{enumerate}
\item We create a module \texttt{gaia\_hydras.GFoo}
  (``G'' for \gaia).
\item Inside \texttt{GFoo}, the identifier \texttt{bar}
  is reserved in priority to \gaia's version, and the notation
  \texttt{hbar} is used for \texttt{hydras.Epsilon0.Foo.bar}.
\end{enumerate}
